Thesis Project Proposal Meeting

### 2020-09-13 thesis proposal .Rmd
updated thesis meeting document

# Goals for today's meeting 
1. Discuss project proposal below and the different ways to go
2. 
3. Outline timeline for regular meetings and when milestones for this project should accomplished
4. Discuss appropriate workflow for this project

# Main Objectives: 
What is the single main objective of the research? This needs to relate to some kind of general ecological issue, and be articulated in a single concise statement.

How is environmental variation (temperature, pH, nutrient composition) systematically studied and manipulated across organismal, population, and community ecology and how does study design influence conclusions about environmental variation compare across these bodies of literature?

@@

# Testable hypothesis: A hypothesis or set of hypotheses must:
clearly contribute to achieving the main objective
be able to be definitively tested and rejected
ideally, the set of hypotheses should together support some inference about the main objective.
Generating hypotheses is a challenge. Make sure there are not logical gaps between the
hypotheses, objective and methods used to test them, or if gaps exist, address them.

H0: There is no difference in how variation is studied at different levels of biological organization and thus the conclusions are the same across all levels.

@@

H02: Environmental variation does affect how rate scale across levels of biological organization?

# Methods:

1. I will conduct a series of ISI literature searches to get a hollistic set of studies referencing environmental variation with selected keywords

How will hypotheses be tested? General categories include experiments, observations (surveys),
meta-analyses, analysis of theoretical models. Will inferences be drawn from more than one type
of evidence?
- How will data be collected and analyzed? What statistical tests and software will you use?
- What resources are required? Budget for time (e.g., timeline) and for costs.
#Results: Consider, in advance, the 2-3 key figures or tables you will produce for your final
paper. Sketch them, including axes, and even the data that would reject or fail your hypotheses or
support your predictions.
#Inference and Next Steps: What logical steps will you use to achieve your main objectives,
and draw conclusions? How exactly will your figures (sketched above) answer your original
questions? Consider different possible versions of the results, and how you might interpret them.
Then revisit your questions – are you happy with how your hypotheses are stated, given the
possible results?
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

# Goals for today's meeting 
1. Discuss project proposal below and the different ways to go
2. Discuss how to design proper search term parameters that provides big picture but managable study count
3. Outline timeline for regular meetings and when milestones for this project should accomplished
4. Discuss appropriate workflow for this project

# Main Objectives 
How is environmental variation (temperature, pH, nutrient composition) systematically studied and manipulated across organismal, population, and community ecology and how does study design influence conclusions about environmental variation compare across these bodies of literature?

@@

# Testable hypothesis
H0: There is no difference in how variation is studied at different levels of biological organization and thus the conclusions are the same across all levels.

@@

H02: Environmental variation does not affect how rate scale across levels of biological organization

Ha2: Environmental variation alters how rates scale across levels of biological organization by influencing metabolic rate

# Methods
1. I will conduct a series of ISI literature searches to get a hollistic set of studies referencing environmental variation with selected keywords. I will then select studis based on a stricy set of criteria and enter those studies into a spreadsheet, recording relevant information (study organism, biological organization level, variation type, response variable, ).

Current search term ideas:
* "environmental variability" AND ecology AND temperature (1,281 results)
* "environmental variability" AND ecology (4049 results)
* "environmental variability" AND rate AND ecology (1,062 results)
* "environmental variability" AND ecology AND organism (802 results)
* "environmental variability" AND ecology AND population (2,458 results)
* "environmental variability" AND ecology AND community (1,275 results)
* "environmental variation" AND ecology (4,983 results)

2. I will then synthesize the patterns across studies to address my main objectives. This will culminate in written document summarizing that language used in different sub disciplines as well as the similarities and differences in environmental variability.

3. If there are studies that feature the same type of experimental design, I would like to conduct a meta-analaysis on that particular body of literature in R.

4. If not, I would like to model environmental variability parameters from the different studies using R. (Less sure of how this could be achieved but I'd like to incorporate modelling components to this project)

# Potential Results
```{r, echo = FALSE}
knitr::include_graphics("images/fig 1.png")
```
Figure 1. Quantitative representation of the relatedness of environmental variability study work across different levels of biological organization (modified from http://environmentalcomputing.net/multidimensional-scaling/)

```{r, echo = FALSE}
knitr::include_graphics("images/fig 2.png")
```

Figure 2. Scaling of responses to environmental variability to animal body size (modified from Schramski et al 2015, PNAS)

# Timeline, Inference, and Next Steps
To accomplish this work I'd like to hit the following milestones:

* Narrow in on search terms (end of September)
* Decide on filter to select studies by (end of September)
* Filter through studies (end of fall semester)
* Theoretical foundation of modelling work in the spring (end of October)
* Premilinary literature review summary (end of fall semester)
* Data extraction complete (early March)
* Modelling work (end of March)

Figure 1 above will answer my questions about potential dissonance and gaps in environmental variability across different levels of organization and their respective field of study. An NMDS-like plot would be a quanitative way to display similarities and potential distinctions.

Figure 2 is a simple first pass at potentially looking about how MTE and environmental variability could interact. I'd be really interested in looking into the math for how environmental variability could alter metabolic rate and looking the relationship between body size. I think this sample figure will answer the question of whether or not environmental variability has the ability to scale with rates across levels of organization.
